From Big Data to Big Displays\\ High-Performance Visualization at Blue Brain

### 2017-06-05 paper.tex
Update pdf

%% Author and Affiliation (multiple authors with multiple affiliations)
\author{\small Stefan~Eilemann, Marwan~Abdellah, Nicolas~Antille, Ahmet~Bilgili, Grigory~Chevtchenko, Raphael~Dumusc, Cyrille~Favreau, Juan~Hernando, Daniel~Nachbaur, Pawel~Podhajski, Jafet~Villafranca\thanks{\textit{firstname.lastname}@epfl.ch}}
\institute{Blue Brain Project, Ecole Polytechnique Federale de Lausanne}

@@

This publication was supported by the Blue Brain Project (BBP), the Swiss
National Science Foundation under Grant 200020-129525, the King Abdullah
University of Science and Technology (KAUST) through the KAUST-EPFL alliance for
Neuro-Inspired High Performance Computing, the Spanish Ministry of Science and
Innovation under grant (TIN2010-21289-C02-01/02), the Cajal Blue Brain Project,
Hasler Stiftung Projekt Nr. 12097, and from the European Union’s Horizon 2020
research and innovation programme under grant agreement No 720270 (HBP SGA1).

We would also like to thank the people from GMRV at the Rey Juan Carlos
University (URJC) for their collaboration under the Cajal Blue Brain and HBP
projects.

>>>>

%% Author and Affiliation (multiple authors with multiple affiliations)
\author{Stefan~Eilemann, Marwan~Abdellah, Nicolas~Antille, Ahmet~Bilgili, Grigory~Chevtchenko, Raphael~Dumusc, Cyrille~Favreau, Juan~Hernando, Daniel~Nachbaur, Pawel~Podhajski, Jafet~Villafranca, Felix Sch\"urmann\thanks{\textit{firstname.lastname}@epfl.ch}}
\institute{Blue Brain Project, Ecole Polytechnique Federale de Lausanne}

@@

This publication was supported by the Blue Brain Project (BBP), the Swiss
National Science Foundation under Grant 200020-129525, the King Abdullah
University of Science and Technology (KAUST) through the KAUST-EPFL alliance for
Neuro-Inspired High Performance Computing, the Spanish Ministry of Science and
Innovation under grant (TIN2010-21289-C02-01/02), the Cajal Blue Brain Project,
Hasler Stiftung Projekt Nr. 12097, and from the European Union’s Horizon 2020
research and innovation programme under grant agreement No 720270 (HBP SGA1). We
would also like to thank the people from GMRV at the Rey Juan Carlos University
(URJC) for their collaboration under the Cajal Blue Brain and HBP projects.
